---
title: "W_UP_01"
author: "Ashley Davis"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called push ups from the tiger stats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of push ups of line vs skill players

$H_A$: The average number of push ups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

In this analysis, I will be explaining whether there is a statistical difference in the average number of push ups done by line players and skill players. The method used will be the variable analysis of "Numerical~Categorical," shown as "PushUps~Position" to demonstrate.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

In this table, it is shown that the average amount of push ups completed by a player in a "Line" position is 17.1. Compared to the average amount of push ups of that of a player in a "Skill" position, which is 49.7. This demonstrates a clear differentiation in the amount of pushups that can be completed between the two types of players, proving that skill players can do more pushups than the line players.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisies the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The Welch Two Sample t-test expresses the p-value as 0.000009421. The insignificance of the p-value proves that there is a true difference in the average amount of push ups completed by either a line player or a skill player. Skill players are doing 3 times more push ups than the line players, concluding that we must reject the null hypothesis.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason. Watch the chapter 6 videos from the George Town videos collection.!-->

Based on the research conducted, it is concluded that we must reject the null hypothesis due to the insignificance of the p-value. Thus, the average number of push ups done by line players is statistically different than that of skill players. On average, the skill players can do three times more push ups than the line players. 
